### 2017-02-23 R/ITHIM.Rmd
Updated deltaBurden to work with new version

  DALYs <- lapply(ITHIMList, deltaBurden, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}

>>>>

  DALYs <- lapply(ITHIMList, deltaBurden, baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal <- rbind(DALYsTotal, DALYs)
}
